\documentclass[13pt,a4paper,roman]{moderncv}      
\moderncvstyle{banking}                           
\moderncvcolor{black}                             
\nopagenumbers{}                                  
\usepackage[utf8]{inputenc}
\usepackage{fontawesome}
\usepackage{fontspec}
\usepackage{tabularx}
\usepackage{ragged2e}
\usepackage[scale=0.91]{geometry}
\usepackage{multicol}

\usepackage{import}
% personal datahttps://www.overleaf.com/project/60eb5099143ba4806c917576
\name{AADARSH}{BISHEN}
\address{}{}{}
\newcommand*{\customcventry}[7][.3em]{
  \begin{tabular}{@{}l} 
    {\bfseries #4}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\bfseries #5}
  \end{tabular} \\
  \begin{tabular}{@{}l} 
    {\itshape #3}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\itshape #2}
  \end{tabular}
  \ifx&#7&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#7%
    \end{minipage}}\fi%
  \par\addvspace{#1}}

\newcommand*{\customcvproject}[4][.25em]{
%   \vfill\noindent
  \begin{tabular}{@{}l} 
    {\bfseries #2}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\itshape #3}
  \end{tabular}
  \ifx&#4&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#4%
    \end{minipage}}\fi%
  \par\addvspace{#1}}

\setlength{\tabcolsep}{12pt}

\begin{document}
\makecvtitle
\vspace*{-23mm}

\begin{center}
\begin{tabular}{ c c c }
  \faEnvelopeO\enspace bishen@iitk.ac.in & \faGithub\enspace https://github.com/bishen28 & \faMobile\enspace 8858428707\\  
\end{tabular}
\end{center}

\section{EDUCATION}

\begin{tabular}{|p{3cm}|p{7cm}|p{2.6cm}|p{3cm}|}
 \hline 
   \textbf{Degree} &  \textbf{Institute} & \textbf{Year} & \textbf{CPI or \%}\\
 \hline B.T\textbf{(Civil Engg.)} & Indian Institute of Technology Kanpur & 2018-Present & 6.6 \\
 \hline
 Class XII &  GA Inter High School, Hajipur(BSEB) & 2017 & 65.8\% \\
 \hline
 Class X &   GA Inter High School, Hajipur(BSEB) & 2015 & 75.8\% \\
 
 \hline
\end{tabular}




\section{SCHOLASTIC ACHIEVEMENT}


  {\begin{itemize}
    \item \large Secured  \textbf{All  India  Rank 3177} in \textbf{Joint Entrance Examination Advanced - 2018} among  250000  candidates.
    \item \large Secured \textbf{All India Rank 4554} in \textbf{Joint Entrance Examination Mains - 2018} among 1.5 million candidates.
  \end{itemize}
  }


\section  {PROJECTS}

{\customcvproject {\large SORTING VISUALIZER (self project)}{Aug 2021 - Present}
  {\begin{itemize}
    \item  \large Created a web application using \textbf{HTML}, \textbf{CSS}, \textbf{JavaScript} to visualize how various sorting work. 
    \item \large Learnt \textbf{Sorting Algorithm} like Bubble sort, Insertion Sort, Selection Sort, Quick Sort, Merge Sort.
    \item \large Created \textbf{User Interface (UI)} using \textbf{HTML}, \textbf{CSS} and enhanced it further using \textbf{Bootstrap}.
    \item \large Implemented the \textbf{animation}, \textbf{color effect} and core functionality using \textbf{JavaScript}
  \end{itemize}
  }
}

{\customcvproject{\large BUDGET MANAGER (self project)}{July 2021–Aug 2021}
{\begin{itemize}
  \item \large Build a {browser action chrome extension} using \textbf{chrome Application programming interface(API)} 
  \item \large Used \textbf{Manifest Version-2}, and \textbf{Chrome APIs like chrome.storage, contextmenu, and notifications}.
  \item \large This Extension \textbf{helps to keep track of Expenditure} while shopping on multiple e-commerce website.  
  \item \large You can set the limit of your Expenditure and whenever you cross the limit it will notify.   
\end{itemize}
}
} 
 

{\customcvproject{\large SIMON GAME (self project)}{June 2021 – July 2021}
{\begin{itemize}
  \item \large Build \textbf{web version} of exact physical electronic The Simon Game for memory skill development.
  \item \large  Learnt  advanced JavaScript HTML \textbf{document object modal(DOM)} and implemented in the project.
  \item \large People can play this game online and can \textbf {save a lot of money}, instead of buying the physical toy.
\end{itemize}
}
}


{\customcvproject{\large LEADS TRACKER - A chrome Extension (self project)}{June 2021 – July 2021} 
{\begin{itemize}
  \item \large Build the extension and \textbf{deployed} it on \textbf{chrome web store}, peoples can store and delete URL in one click.  
  \item \large This extension will \textbf{help the sales company}, they can store the profile-URL of their potential customers.
\end{itemize}
}
}

{\customcvproject{\large VERTICAL LIFT MACHINE}{Aug 2019 – Nov 2019} 
{\large {under prof. Mohit Law Department of Mechanical Engineering, IIT Kanpur}}

{\begin{itemize}
  \item \large Made a  lefting machine (course project) under a project head and worked with 6 other people.
  \item \large Made \textbf{3D-CAD} modal of  project and Learnt controlling a \textbf {DC motor} using a  \textbf{Arduino board}.
\end{itemize}
}
}

\section{TECHNICAL SKILL}
\begin{minipage}{\maincolumnwidth}%
	\small{
    	\begin{itemize}
          
          \item \large \textbf{Programming Languages :} C, C++, HTML, CSS, JavaScript, Familier with python 
         \item \large \textbf{Tool\textbackslash Framework\textbackslash library :} MATLAB, Autodesk Inventor, Ms-Office, LaTeX, Bootstrap, jQuery 
		\end{itemize}}% 
\end{minipage}%

\section{RELEVANT COURSEWORK {(*online course )}}
\begin{minipage}{\maincolumnwidth}
\begin{multicols}{2}
\begin{itemize}
  \large {
    \item Fundamental of Computing
    \item Probability and Statistics
    \item Computational Methods in Engineering
    \item Data Structures and Algorithms* 
    \item Object-Oriented Programming* 
    }
\end{itemize}
 \end{multicols}
\end{minipage}

\section{MISCELLANEOUS}
\begin{minipage}{\maincolumnwidth}
	
	\small{
    	\begin{itemize}
          \item  \large Achieved \textbf{1584 (2-star)} rating in \textbf{Competitive Programming} contest platform codechef.

          
          \item \large Worked as \textbf{Teaching Assistant} at Shiksha Sopan(classes for Sopan children by H.C Verma).
          
          \item  \large Participated in volleyball tournament in \textbf{Inferno'18}, an inter-hostel sports event and \textbf {won gold medal.} 
          \item  \large Participated in volleyball tournament in \textbf{Udghosh'18}, an collage sportsfest  and \textbf {won Silver medal.} 
          
          
          
		\end{itemize}
		}
		
\end{minipage}
      

\nocite{*}
\bibliographystyle{plain}
\bibliography{publications}                       
\end{document}
